%!TEX TS-program = xelatex
% vim: set fenc=utf-8

% -*- coding: UTF-8; -*-
%!TEX encoding = UTF-8
\documentclass[twoside]{CUGThesis}

\title{基于U-Net网络的遥感图像语义分割} %论文题目
\author{郭子睿} %作者姓名
\date{\today} %日期，默认当日
\school{计算机学院} %院系名称
\classnum{计算机科学与技术} %专业
\stunum {20151003952} %学号
\instructorone{李显巨} %指导教师1姓名
\instructoronelevel{副教授}

\usepackage{makecell}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{hyperref}

\begin{document}
\maketitle
\makestatement

\begin{cnabstract}{U-Net；语义分割；遥感图像}
	在计算机视觉中，图像分割是将数字图像细分为多个图像子区域的过程。分割的目标是将图像的表示更改为更有意义且更易于分析的内容。更确切地说，图像分割是对图像中的每个像素打上标签的过程，相同标签的像素有某些相似的视觉特征。

	遥感图像分割主要目的是在遥感图像中定位诸如道路、房屋、林业资源的物体以达到统计国土资源或进行土地规划的目的。遥感图像尺寸巨大，内容复杂。传统遥感图像分割主要依赖人工标注，工作量大。因此，开发一种自动遥感图像分割算法是十分有必要的。

	本文尝试使用U-Net对遥感图像进行语义分割，并对使用U-Net进行遥感图像语义分割的可行性做出了评估。
\end{cnabstract}

\begin{enabstract}{U-Net; Semantic Segmentation; Remote Sensing Image}
	In the field of computer vision,image segmentation is refered to partitioning a digital image into multiple areas. The aim of segmentation is to simplify and change the representation of an image into something that is more meaningful and easier to analyze.More specificly, image segmentation is the process of assigning a label to every pixel in an image such that pixels with the same label share certain characteristics.

	The main purpose of remote sensing image segmentation is to locate objects such as roads, houses, and forestry resources in remote sensing images to achieve the purpose of statistical land resources or land planning. Remote sensing images are large in size and complex in content. Traditional remote sensing image segmentation mainly relies on manual labeling and has a large workload. Therefore, it is very necessary to develop an automatic remote sensing image segmentation algorithm.

	This paper attempts to use Semantic Separation of Remote Sensing Images by U-Net and evaluates the feasibility of using U-Net for semantic segmentation of remote sensing images.
\end{enabstract}

\makeToc

%---------------------------------------------开始正文---------------------------------------------
\include{chap1}
\include{chap2}
\include{chap3}

%---------------------------------------------  致谢  ---------------------------------------------
\begin{spacing}{2}
	\section*{致谢}
	感谢妈妈把我生养得这么好。
\end{spacing}
\phantomsection
\addcontentsline{toc}{section}{致谢}

\clearpage
%---------------------------------------------参考文献---------------------------------------------

\bibliography{Bibs/mybib}
\phantomsection
\addcontentsline{toc}{section}{参考文献}

\end{document}